Regularising Lotka--Volterra interaction matrices by species grouping: optimal groupings are unpredictable

### 2022-03-20 article.rnw
Add a possible TODO to the introduction.
Add a sentence to reiterate the overall premise at the beginning of the discussion.
Make the first paragraph of the discussion less pessimistic.

We propose that species might be best partitioned into groups without regard to any \emph{a priori} definition but instead based purely upon which grouping gives the most parsimonious model.
% DBS: We can say something here about how this data-informed approach has worked very well for other clustering problems, such as modularity in networks. I can point to some very good references along those lines.
In this study, we investigate the usefulness and correctness of such an approach using experimental \emph{Drosophila} fecundity data provided by \textcite{terry2021natural}.
We fit the Lotka--Volterra model, with grouped species, to find the grouping that gives the most parsimonious model.
We group species independently with regard to their effects upon other species and their responses to other species, to find whether the appropriate groupings might differ for these two cases.

@@

% DBS: I would start this paragraph with a restatement of the overall premise.
The results show that grouping the interaction coefficients of species was likely to give a more parsimonious model (probability \probnum{\Sexpr{sum(brute_data$statistics$aic_weight[brute_data$statistics$aic < brute_data$fully_separated_statistics$aic])}}) than leaving them ungrouped, but not confidently so.
Which grouping might give the most parsimonious model also could not be determined with any confidence.
% DBS: The two preceding sentences are very glass half empty. I'm also not sure that the results are really so equivocal. What makes you feel this way?
The intransitivity of coclassification in some instances even suggests that there may not be a single ``best'' grouping, but rather two or more quite distinct and mutually exclusive groupings of similar validity.
% DBS: In my mind, I would steal the preceding sentence and spin it potentially spin it into its own paragraph later since it speaks strongly to a mixed-membership approach which could be sold as a "future direction".

>>>>

We propose that species might be best partitioned into groups without regard to any \emph{a priori} definition but instead based purely upon which grouping gives the most parsimonious model.
% DBS: We can say something here about how this data-informed approach has worked very well for other clustering problems, such as modularity in networks. I can point to some very good references along those lines.
In this study, we investigate the usefulness and correctness of such an approach using experimental \emph{Drosophila} fecundity data provided by \textcite{terry2021natural}.
We fit the Lotka--Volterra model, with grouped species, to find the grouping that gives the most parsimonious model.
We group species independently with regard to their effects upon other species and their responses to other species, to find whether the appropriate groupings might differ for these two cases.
%TODO: Mention the comparison to traits (body size)?

@@

We have shown that it is possible to fit a more parsimonious model of species interactions by grouping the interaction coefficients of species \emph{a posteriori}, and hence reducing the number of free parameters in the model.
Indeed, the results show that grouping species was likely to give a more parsimonious model (probability \probnum{\Sexpr{sum(brute_data$statistics$aic_weight[brute_data$statistics$aic < brute_data$fully_separated_statistics$aic])}}) than leaving them ungrouped.
Which grouping would give the most parsimonious model, however, could not be determined with confidence.
The intransitivity of coclassification in some instances even suggests that there may not be a single ``best'' grouping, but rather two or more quite distinct and mutually exclusive groupings of similar validity.
% DBS: In my mind, I would steal the preceding sentence and spin it potentially spin it into its own paragraph later since it speaks strongly to a mixed-membership approach which could be sold as a "future direction".
